### 2025-05-19 paper/main.tex
QGARS pipeline latex

@@

%============================================
% INTRODUCTION
%============================================
\section{Introduction}
\subsection{Background and Motivation}
\subsection{Challenges in Quantum-Classical Hybrid Systems}
\subsection{Contributions of This Work}

>>>>

% Add TikZ package and necessary libraries
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,backgrounds,shapes.geometric}

% Add circuitikz package for circuit diagrams
\usepackage{circuitikz}

% Add float control parameters to help with figure placement
\renewcommand{\floatpagefraction}{0.8}
\renewcommand{\topfraction}{0.8}
\renewcommand{\bottomfraction}{0.8}
\renewcommand{\textfraction}{0.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

% Force LaTeX to place figures earlier
\renewcommand{\dblfloatpagefraction}{0.7}
\renewcommand{\dbltopfraction}{0.8}

@@

%============================================
% INTRODUCTION
%============================================
\section{Introduction}

\subsection{Background and Motivation}

In this paper, we introduce the Quantum Guided Autoencoder with Reservoir Surrogate (QGARS) architecture, illustrated in Fig.~\ref{fig:system_architecture}. This approach combines classical deep learning with quantum reservoir computing to enable efficient medical image classification.

\subsection{Challenges in Quantum-Classical Hybrid Systems}
\subsection{Contributions of This Work}
